---
title: "Using `sessionDiffo`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using_sessionDiffo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# How?

```{r setup}
library(sessionDiffo)
```

# Why?

Ever encountered a situation where the configuration of two systems is different?

Examples:

- a newer package introduced changes in the functionality, and you have different setups on different machines. You might want to pinpoint what is different

- debugging/reporting an issue: you encounter a bug, or someone reports it to you, and you want to compare the full set of packages that are available in the two different setups

# What

## From the command line

```{r}
si1_output <- system.file("extdata", "si1.txt", package = "sessionDiffo")
si2_output <- system.file("extdata", "si2.txt", package = "sessionDiffo")

si1 <- parse_si(si1_output)
si2 <- parse_si(si2_output)

comparison_df <- compare_si(si1, si2)

knitr::kable(comparison_df)
```

## With `ssd`

... standing for `ShinySessionDiffo`

```{r}
if(interactive())
  ssd()
```


# Session info {-}

Ok, this time it is only one. So here there is no need of `sessionDiffo`

```{r}
sessionInfo()
```

